RF pathway abundance

### 2019-11-17 scripts/06_lefse_res_ggplot.Rmd
update

```{r}
CR <- feature %>% 
  filter(str_detect(group, pattern = 'Disease_Class$')) %>% 
  filter(group == 'CR__Disease_Class') %>% 
  ggplot(aes(x = reorder(pathway, score), y = score, fill = direction)) +
            geom_bar(position = position_dodge2(preserve = "single"), stat = 'identity') +
            coord_flip() +
            scale_color_manual(values = c('#00468B', '#EC0000'))  +
            scale_fill_manual(values = c('#00468B', '#EC0000')) +
            theme_minimal() +
            theme(axis.title.y  = element_blank(), 
                  legend.position="bottom") +
            labs(title = str_glue('Response to Complete Response') ,
                 y = 'Score')

tox <- feature %>% 
  filter(str_detect(group, pattern = 'Disease_Class$')) %>% 
  filter(group == 'Toxicity__Disease_Class') %>% 
  ggplot(aes(x = reorder(pathway, score), y = score, fill = direction)) +
            geom_bar(position = position_dodge2(preserve = "single"), stat = 'identity') +
            coord_flip() +
            scale_color_manual(values = c('#00468B', '#EC0000'))  +
            scale_fill_manual(values = c('#00468B', '#EC0000')) +
            theme_minimal() +
            theme(axis.title.y  = element_blank(), 
                  legend.position="bottom") +
            labs(title = str_glue('Response to Toxicity') ,
                 y = 'Score')

g <- plot_grid(CR, tox,
          nrow = 2, 
          align = 'hv',
          labels = 'AUTO',
          axis = 'b')  +
  ggsave('../figs/dtes.jpg', width = 13, height = 12, dpi = 300)
```

>>>>

```{r}
CR <- feature %>% 
  filter(group == 'CR__Disease_Class') %>% 
  ggplot(aes(x = reorder(pathway, score), y = score, fill = direction)) +
            geom_bar(position = position_dodge2(preserve = "single"), stat = 'identity') +
            coord_flip() +
            scale_color_manual(values = c('#ED0000', '#00468B'))  +
            scale_fill_manual(values = c('#ED0000', '#00468B')) +
            theme_minimal() +
            theme(axis.title.y  = element_blank(), 
                  legend.position="bottom") +
            labs(title = str_glue('Response to Complete Response') ,
                 y = 'Score')+ 
            ylim(-4,4) +
            ggsave(str_glue('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/humann2_shotgun/figs/lefse_results_ggplot_recreate/Response to CR.jpg'),  width = 12, dpi = 300 )

tox <- feature %>% 
  filter(group == 'Toxicity__Disease_Class') %>% 
  ggplot(aes(x = reorder(pathway, score), y = score, fill = direction)) +
            geom_bar(position = position_dodge2(preserve = "single"), stat = 'identity') +
            coord_flip() +
            scale_color_manual(values = c('#0099B4', '#AD002A'))  +
            scale_fill_manual(values = c('#0099B4', '#AD002A')) +
            theme_minimal() +
            theme(axis.title.y  = element_blank(), 
                  legend.position="bottom") +
            labs(title = str_glue('Response to Toxicity') ,
                 y = 'Score')+ 
            ylim(-4,4) +
            ggsave(str_glue('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/humann2_shotgun/figs/lefse_results_ggplot_recreate/Response to tox.jpg'),  width = 12, dpi = 300, height = 3.5)

### 2019-11-17 scripts/16_RF_pathway.Rmd
update

```{r}
# load the pheno
pheno <- read_csv('../data/cleaned_pheno/final_pheno.csv') %>% 
  select(-CAR_Group, -Censor_reason ) %>% 
  mutate_at(vars(str_which(names(.),'Sampleid', negate = T)), factor)

# the pathway abundance table
pabun <- read_tsv('../data/humann2_res/humann2_final_out/humann2_pathabundance_cpm_unstratified.tsv') %>% 
  rename(pathway = names(.)[1]) %>% 
  rename_all(funs(str_replace(., '_Abundance$',''))) %>% 
  # remove the unmapped and the unintegrated record
  filter(!pathway %in% c('UNMAPPED','UNINTEGRATED'))

pabun <- bind_cols(pabun[,1],pabun[,pheno$Sampleid])

pabun_rf <- pabun %>% 
  column_to_rownames('pathway') %>% 
  as.matrix() %>% 
  t

all.equal(rownames(pabun_rf), pheno$Sampleid)

tox_RF_PW <- randomForest(pabun_rf, factor(pheno$Toxicity), importance = T)

impor_pw <- importance(tox_RF_PW, type=1) %>% 
  as.data.frame() %>% 
  rownames_to_column(var = 'pathway') %>% 
  arrange(MeanDecreaseAccuracy) 
```

>>>>

```{r}
pheno <- read_csv('../data/cleaned_pheno/final_pheno.csv')

pw <- read_tsv('../data/humann2_res/humann2_final_out/humann2_pathabundance_cpm_unstratified.tsv') %>% 
  rename(pathway = names(.)[1]) %>% 
  rename_all(funs(str_replace(., '_Abundance$',''))) %>% 
  # remove the unmapped and the unintegrated record
  filter(!pathway %in% c('UNMAPPED','UNINTEGRATED'))

pw <- bind_cols(pw[,1],pw[,pheno$Sampleid])

pw_rf <- pw %>% 
  column_to_rownames('pathway') %>% 
  as.matrix() %>% 
  t

all.equal(rownames(pw_rf), pheno$Sampleid)

tox_RF_PW <- randomForest(pw_rf, factor(pheno$Toxicity), importance = T)
```
